Reproducible Research Practices and Barriers to Reproducible Research in Geography: Insights from a Survey

### 2022-10-12 docs/manuscript/manuscript.tex
Minor additions to direct/indirect section

There are several ways to assess the reproducibility of research.
The most direct approach is to simply conduct a study that follows the methods of an existing study and then compare the results of the new study to the results of the old study.

\subsection*{Direct Reproducibility Assessments}
Direct reproducibility assessments can be implemented in two ways: as a one-to-one comparison, in which a single reproduction is used to assess the results and inferences of one prior study; or as a many-to-one comparison, in which teams of researchers attempt multiple parallel reproductions and make a set of comparisons and a collective assessment of one prior study.
Published reproductions of both forms are becoming increasingly common in many disciplines \citep[e.g.,][]{begley2012raise, camerer2016evaluating, camerer2018evaluating, wagenmakers2016registered}. 
However, the researchers conducting those studies have generally only able to partially reproduce study results, often observing small effect sizes.

@@

\subsubsection{Geog Indirect}
To date only a handful studies have tried to indirectly measure the reproducibility of geographic research.
In a survey of participants from the 2016 European Geosciences Union General Assembly, \citet{konkol2019} assessed the frequency with which researchers published their work in ways that enabled computational reproducibility. 
Those authors found that only 33 percent of respondents included links to the data used in their analyses and only 12 percent provided their analytical code. 
The authors also found that only seven percent of respondents ever attempted to reproduce the work of other researchers.
For example, \citet{ostermann2017} use a literature review of volunteered geographic information research publications to assess computational reproducibility based on availability of original data, metadata, source code, or pseudocode.

>>>>

The most direct approach is to simply conduct a study that follows the methods of an existing study and then compare the results of the new study to the results of the old study.

\subsection*{Direct Reproducibility Assessments}
Direct reproducibility assessments can be implemented in two ways: as a one-to-one comparison, in which a single reproduction is used to assess the results and inferences of one prior study; or as a many-to-one comparison, in which teams of researchers attempt multiple parallel reproductions and make a set of comparisons and a collective assessment of one prior study.
Published reproductions of both forms are increasingly common in many disciplines \citep[e.g.,][]{begley2012raise, camerer2016evaluating, camerer2018evaluating, wagenmakers2016registered}. 
However, the researchers conducting those studies have generally only able to partially reproduce study results, often observing small effect sizes.

@@

\subsubsection{Geog Indirect}
To date only a handful studies have tried to indirectly measure the reproducibility of geographic research.
In a survey of participants from the 2016 European Geosciences Union General Assembly, \citet{konkol2019} assessed the frequency with which researchers published their work in ways that enabled computational reproducibility. 
Those authors found that only 33 percent of respondents included links to the data used in their analyses and only 12 percent provided their analytical code. 
The authors also found that only seven percent of respondents ever attempted to reproduce the work of other researchers.
For example, \citet{ostermann2017} use a literature review of volunteered geographic information research publications to assess computational reproducibility based on availability of original data, metadata, source code, or pseudocode.
Remote Sensing survey.
